\section{GMPEs in OpenQuake}
\label{app:gmpes}
The list of currently supported GMPEs is the following:
\begin{itemize}
\item \Verb+AB_2003_AttenRel+: implements the GMPE described in "Empirical Ground Motion Relations for Subduction-Zone Earthquakes and their application to Cascadia and other regions", Gail M.Atkinson and David M. Boore, Bulletin of the Seismological Society of America, Vol. 93, No. 4, pp 1703-1729, (2003).  It also considers the: "Erratum to 'Empirical Ground Motion Relations for Subduction-Zone Earthquakes and their application to Cascadia and other regions'", Gail M. Atkinson and David M. Boore, Vol. 98, No. 5, pp.2567-2569, 2008. The GMPE implements the global model but not the corrections for Japan/Cascadia.
\item \Verb+AS_1996_AttenRel+: implements the GMPE (for horizontal component) described in "Empirical ground motion models", Abrahamson, N. A. and Silva, W. J. Report to Brookhaven National Laboratory, (1996). Reported in: Stewart J. P., Chiou S.-J., Bray J. D., Graves R. W., Somerville P. G., and Abrahamson N. A., 2001. Ground motion evaluation procedures for performance-based design. PEER Report 2001/09, Pacific Earthquake Engineering Research Center, College of Engineering, University of California, Berkeley, USA.
\item \Verb+AS_2008_AttenRel+: implements the GMPE described in "Summary of the Abrahamson and Silva NGA Ground-Motion Relations", Abrahamson, N. A., and W. J. Silva, Earthquake Spectra, 24(1), 67-97 (2008).
\item \Verb+Abrahamson_2000_AttenRel+: implements the GMPE described in: "Effects of rupture directivity on probabilistic seismic hazard analysis", Abrahamson, N. A., Proceedings of the 6th International Conference on Seismic Zonation, Palm Springs, CA, Earthquake Engineering Research Institute (EERI) (2000).
\item \Verb+AkB_2010_AttenRel+: implements the GMPE described in: "Empirical Equations for the Prediction of PGA , PGV, and Spectral Accelerations in Europe, the Mediterranean Region, and the Middle East", Sinnan Akkar, Julian J. Bommer, Seismological Research Letters Vol. 81, No 2,  pp 195-206, March-April (2010).
\item \Verb+BA_2008_AttenRel+: implements the GMPE described in: "Ground-Motion Prediction Equations for the Average Horizontal Component of PGA, PGV, and 5\%-Damped PSA at Spectral Periods between 0.01 s and 10.0 s",  Boore, D. M. and Atkinson, G. M, Earthquake Spectra, Volume 24, Number 1, pp. 99-138 (2008).
\end{itemize}