%
% ------------------------------------------------------------------------------
	\index{PSHA!Input model}
%
OpenQuake requires two main information blocks to perform a calculation: (1) 
a PSHA input model and (2) Calculation Settings.

A PSHA input model defines the properties of the seismic sources 
of engineering  interest within the region considered in the analysis and the 
models capable to describe - once a rupture occurred in a given position - the 
properties of the shaking expected at the site. 
%
A PSHA input model contains two main objects: the \emph{Seismic Sources System} 
and the \emph{Ground Motion Models System}. 
%
The former specifies location, geometry, and seismicity properties of seismic 
sources and potential epistemic uncertainties affecting this information. 
%
The latter describes the details of the ground motion prediction equations to 
be adopted in the calculation and the related epistemic uncertainties. 
%
Therefore, OpenQuake PSHA input models are always defined using two logic 
tree structures, one describing epistemic uncertainties associated with the 
creation of the ERF - called \emph{Seismic Sources logic tree} - 
	\index{Logic Tree!Seismic sources}
the other - called \emph{Ground Motion Models logic tree} - takes into account 
the uncertainties connected with the use of models capable to predict the 
expected ground motion at the site. 
	\index{Logic Tree!Ground Motion Models}
%
In cases where the epistemic uncertainties are not considered, the logic tree 
structure simply consists of one branching level with just one branch (with 
weight equal to 1).

Calculation settings specifies for example the typology of results required,
the site or the sites where to compute the hazard, the methodology to apply.

The organisation of this chapter is the following. The next section offers
further explanations about the way we describe and model logic trees. 
Section \ref{hazard:seismic_source_types} contains a description of the seismic
source type currently supported by OpenQuake while section 
\ref{hazard:seismic_source_types} provides a short description of the 
ground motion models currently supported. Finally, section 
\ref{hazard:calculation_settings} provides an outlook of the hazard 
specific calculation setting supported by OpenQuake.
%
% ------------------------------------------------------------------------------
\input{./Part_Hazard/unifiedmodel/logicTrees.tex}
\clearpage
% ------------------------------------------------------------------------------
%
% ------------------------------------------------------------------------------
\input{./Part_Hazard/unifiedmodel/seismicSourceTypes.tex}
%
% ------------------------------------------------------------------------------
\section{GMPEs description}
\label{hazard:gmpe_selection}
OpenQuake provides only hardcoded Ground Motion Prediction Equations and misses 
of a mechanisms allowing the user to specify new GMPEs. This is something the 
OpenQuake team may think to introduce in the future. 

For the time being the user in need of a specific Intensity Measure 
Relationship, can:
\begin{itemize}
\item Fork the OpenQuake project from the OQ repository\footnote{The 
OpenQuake software repository can be reached here: 
\hfill \newline  https://github.com/gem/openquake/}, code the new GMPE 
following the examples available in the OpenQuake and OpenSHA repository 
and, - if he's willing to share his contribution with the other OQ users - 
ask to push his modified version of OpenQuake. 
\item Post a ticket on the OpenQuake website \marginpar{this is something 
I need to check with Ben} 
\end{itemize}

Table \ref{tab:OQ_GMPEs} provides a list of the Ground Motion Prediction 
Equations supported. The vast majority are GMPEs implemented in OpenSHA 
with just a couple of developed in the course of the GEM1 project. 
New GMPEs are expected to be added soon with the contribution of 
some GEM's Regional Programmes.
%
\begin{table}[!t]
\centering
\begin{tabular}{llll} \hline
% >>> Table header
\textbf{Ground Motion Prediction} & \textbf{IMTs} & \textbf{Component } & \textbf{ID} \\
\textbf{Equation}& & \textbf{type} & \\ 
\hline
% <<< Table header
\cite{atkinson2006} & PGA & & AtkBoo06 \\
\cite{abrahamson2008} & PGA & & AS2008 \\
\cite{boore2008}  & PGA,PGV,S$_{a}$ & Avg Hor & BA2008 \\
\cite{chiou2008}  & PGA,S$_{a}$ &  & CY2008 \\
\cite{zhao2006}  & PGA,S$_{a}$ &  & ZhaoEtAl2006 \\
\hline
\end{tabular}
\caption{Some of the Ground Motion Prediction Equations (in the OpenSHA 
terminology Intensity Measure Relationship) currently included in OpenSHA 
and OpenQuake.}
\label{tab:OQ_GMPEs}
\end{table}
%
%
% ------------------------------------------------------------------------------
\section{Calculation settings description}
\label{hazard:calculation_settings}
%



